%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
    \newcommand{\resumeSubHeadingListEnd}{\vspace{-10pt}\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Siksha 'O' Anusandhan University (ITER)}{Nov. 2021 -- June 2025}
{{Bachelor of Technology in Computer Science Engineering}}{ \textbf{CGPA: 9.85} }
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{\textbf{Member of Technical Staff}}{March 2025 - Present}
{\href{https://avetilearning.com/}{\textbf{Aveti Learning Pvt. Ltd.}}}{Bhubaneswar, India}
\resumeItemListStart
\resumeItem{  Designed and implemented the backend for teachers’ app using \textbf{FastAPI} and \textbf{PostgreSQL}, with deployment and orchestration on \textbf{Kubernetes} for scalability and fault tolerance.}
\resumeItem{Self-hosted a scalable \textbf{video conferencing platform} using \textbf{Jitsi Meet}, orchestrated via \textbf{Kubernetes} and \textbf{Helm charts}, implementing dynamic auto-scaling and reducing cloud infrastructure cost by \textbf{80\%}.}
\resumeItem{ Developed and optimized microservices for the platform serving \textbf{2700+ schools} and \textbf{200K+ students}, leveraging \textbf{AWS}, \textbf{Docker}, and \textbf{CI/CD pipelines} to ensure high availability and performance.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{\textbf{Software Engineer Intern}}{June 2024 -- Dec 2024}
{\href{https://research.samsung.com/sri-b}{\textbf{Samsung R\&D Institute}}}{Bangalore, India}
\resumeItemListStart
\resumeItem{ Developed a static power analysis tool to identify performance bottlenecks and reduce power inefficiencies by \textbf{10\%}, leveraging in-house \textbf{GenAI} for optimization suggestions.}
\resumeItem{ Engineered an industry-first ground truth generation framework for \textbf{ARM}, achieving \textbf{91\% accuracy} in per-instruction energy measurement, with support for both hardware and software modes.}
% \resumeItem{ Automated the build process for \textbf{C/C++} using \textbf{CMake}, reducing compilation time by \textbf{70\%}.}
\resumeItem{ Created an automation suite using \textbf{Python} and \textbf{Java} for capturing and analyzing per-instruction power consumption, reducing ground truth creation time by \textbf{90\%}.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{\textbf{Software Developer Intern}}{Sep. 2022 - May 2024}
{\href{https://avetilearning.com/}{\textbf{Aveti Learning Pvt. Ltd.}}}{Bhubaneswar, India}
\resumeItemListStart
\resumeItem{ Developed a cross-platform AI tutor bot for mobile and web using \textbf{Flutter}, leveraging \textbf{Langchain} and \textbf{OpenAI GPT-4} as a backend service.}
\resumeItem{ Integrated \textbf{vector search}, and \textbf{Retrieval-Augmented Generation (RAG)} for question answering (QA) in chatbot.}
\resumeItem{Optimized \textbf{CI/CD} deployment pipelines using \textbf{GitHub Actions}, reducing deployment time by \textbf{50\%}.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://github.com/AM-ash-OR-AM-I/Passlock}{\underline{Passlock}} \& \href{https://github.com/AM-ash-OR-AM-I/PasslockDesktop}{\underline{PasslockDesktop}}} $|$ \textbf{Python, Firebase, Kivy}}{Jan. 2022 -- June 2022}
\resumeItemListStart
\resumeItem{Created a cross-platform password manager for mobile and desktop (Android, Linux, Windows, MacOS).}
\resumeItem{Leveraged \textbf{Firebase} real-time database for efficient CRUD operations.}
\resumeItem{Implemented \textbf{AES-256 encryption} to ensure robust password security and decryption.}
\resumeItem{Designed real-time password synchronization system across devices with \textbf{0ms latency}.}
\resumeItem{Optimized app load time by \textbf{30\%} implementing lazy loading technique.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- Skills -----------
\vspace{-10px}
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, Java, C, C++, Dart, Assembly, LaTeX} \\
        \textbf{Frameworks \& Libraries}{: Flutter, FastAPI, Flask, Kivy, Langchain, NumPy, Pandas} \\
        \textbf{Tools \& OS}{: Linux, Bash, UNIX Shell, Git, SSH, GitHub Actions, Nmap} \\
        \textbf{Cloud \& DevOps}{: AWS, Microsoft Azure, Google Cloud Platform, Docker, Kubernetes} \\
        \textbf{Databases}{: Oracle DB, PostgreSQL, MySQL} \\
        }}

\end{itemize}

%----------- Achievements -----------
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        Finalist in \textbf{JP Morgan Chase Code For Good} \\
        Secured \textbf{4th} rank in \textbf{Capture The Flag} contest conducted by \textbf{NIT Rourkela} \\
        Rated \textbf{1762 (Max)} in \href{https://www.codechef.com/users/ashu2909}{\underline{CodeChef}} \\
        Rated \textbf{1713} in \href{https://leetcode.com/ashu_coder/}{\underline{LeetCode}} \\
        Rated \textbf{1232 (Max) Pupil} in \href{https://codeforces.com/profile/ashucoder}{\underline{CodeForces}} \\
  }}
\end{itemize}